
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment9.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19. 
```{r}
library(gganimate)
library(ggplot2)
library(tidyverse)
library(lubridate)
df <- read_csv("https://covid19.who.int/WHO-COVID-19-global-data.csv")

df %>%filter(Date_reported=='2021-10-17') %>% arrange(-Cumulative_deaths)
```
The three top countries are USA, Brazil, and India

2. Make a plot revealing the number of deaths in the three countries with the most numbers of deaths
```{r}
df <- na.omit(df)
df$Months=month(df$Date_reported)
df %>%filter(Date_reported>'2021-01-01') %>%  filter(Country_code %in% c('US','BR','IN')) %>% ggplot(df,mapping=aes(y=Cumulative_deaths,
            x=Months,
            color=Country_code))+ 
  geom_line()+
  transition_reveal(Months)
```

3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases? 
```{r}

df$death_per_cases <- df$Cumulative_deaths/df$Cumulative_cases
df %>% filter(Date_reported=='2021-10-17') %>% arrange(-death_per_cases)
```
The three countries with the highest deaths per cases are Yemen, Peru, and Mexico.

4. Make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 
```{r}
df %>%filter(Date_reported>'2021-01-01') %>%  filter(Country_code %in% c('YE','PE','MX')) %>% ggplot(df,mapping=aes(y=death_per_cases,
            x=Months,
            color=Country_code))+ 
  geom_line()+
  transition_reveal(Months)
```

5. Use `transition_reveal` to create three animated graph with the vaccination data at 

https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv
```{r}
df1 <- read_csv('https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv')
df1$MONTHS <- month(df1$Date)
df1 <- na.omit(df1)
df1 %>%filter(Date>'2021-01-01') %>%  filter(Province_State %in% c('New York','California')) %>% ggplot(df,mapping=aes(y=Doses_admin,
            x=MONTHS,
            color=Province_State))+ 
  geom_line()+
  transition_reveal(MONTHS)
```
```{r}
df1 %>%filter(Date>'2021-01-01') %>%  filter(Province_State %in% c('New York','California')) %>% ggplot(df,mapping=aes(y=Doses_alloc,
            x=MONTHS,
            color=Province_State))+ 
  geom_line()+
  transition_reveal(MONTHS)
```
```{r}
df1 %>%filter(Date>'2021-01-01') %>%  filter(Province_State %in% c('Michigan','Florida')) %>% ggplot(df,mapping=aes(y=Doses_shipped,
            x=MONTHS,
            color=Province_State))+ 
  geom_line()+
  transition_reveal(MONTHS)
```

