
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment8.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19.  
```{r}
library(gapminder)
library(gganimate)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(knitr)
df<-read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
df$Month<-month(df$Date_reported)
d1<-df %>% group_by(Month,Country) %>% summarise(avg_death=mean(Cumulative_deaths))
d2<-d1 %>% group_by(Month) %>% mutate(Rank=rank(-avg_death)) %>% ungroup()
d3<-d2 %>% filter(Rank<=10)

g<-d3 %>% ggplot(d3,mapping=aes(x=Rank,y=avg_death,group=Country,fill=Country,label=Country))+geom_col()+geom_text(d3, mapping=aes(y = avg_death, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+ 
    labs(title = 'Month {closest_state}', x='', y='Total Number of Positive Cases', fill='Month')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(Month)+ease_aes("cubic-in-out")
   
animate(g,nframes=100)
```

2. Make another bar race using that dataset.  
```{r}
df<-read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
df$Month<-month(df$Date_reported)
d1<-df %>% group_by(Month,Country) %>% summarise(avg_cases=mean(Cumulative_cases))
d2<-d1 %>% group_by(Month) %>% mutate(Rank=rank(-avg_cases)) %>% ungroup()
d3<-d2 %>% filter(Rank<=10)

g<-d3 %>% ggplot(d3,mapping=aes(x=Rank,y=avg_cases,group=Country,fill=Country,label=Country))+geom_col()+geom_text(d3, mapping=aes(y = avg_cases, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+ 
    labs(title = 'Month {closest_state}', x='', y='Total Number of Positive Cases', fill='Month')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(Month)+ease_aes("cubic-in-out")
   
animate(g,nframes=100)
```

3. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar race from ones in the slides. 
```{r}
df <- read_csv("https://covidtracking.com/data/download/all-states-history.csv")
df$week <- week(df$date)
d1 <- df %>% group_by(week, state) %>% summarise(mean = mean(hospitalizedCumulative, na.rm=TRUE))
d2 <- d1 %>% group_by(week) %>% mutate(rank=rank(-mean)) %>% ungroup()
d3 <- d2 %>% filter(rank <= 10)
a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=state, fill=state, label=state)) + geom_col()+
    geom_text(aes(y = mean, label = state), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Week {closest_state}', x='', y='Total Hospitalized Cases', fill='state')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank(), legend.position = "none") + 
    transition_states(week)+
    ease_aes("cubic-in-out")
animate(a1, nframes = 400)
```

