
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 3. 

-------

Problems
-------
 \

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|------	|-----	|-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|
```{r}
df= data.frame(Rank=c(0:3),Age=c(28,34,29,42),Name=c("Tom",'Jack','Steve','Ricky'))
df
```

2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv)

Show the names of the variables in the data
```{r}
df <- read.csv('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv')
names(df)
```

3. How many columns and rows the data have? 
```{r}
str(df)
```
5 columns and 30869 rows. 

4. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?
```{r}
sum(is.na(df))
colSums(is.na(df))

```
There are no missing values. 

5. What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column. 
```{r}
class(df$date)
df$date=as.Date(df$date)
```

6. Capitalize the names of all the variables
```{r}
names(df)[1]='Date'
names(df)[2]='State'
names(df)[3]='Fips'
names(df)[4]='Cases'
names(df)[5]='Deaths'
str(df)
```

7. Find the average number of cases per day. Find the maximum cases a day.  
```{r}
mean(df$Cases)
max(df$Cases)
```

8. How many states are there in the data?  
```{r}
table(df$State)
```

9. Create a new variable `weekdays` to store the weekday for each rows. 
```{r}
df$Weekdays <- weekdays(df$Date)
```

10. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
-  `no_death` if there is no death that day

Find the frequency and relative frequency of `no_death` and `has_death`. 
```{r}
df$death2 <- ifelse(df$Deaths==0,'no_death','has_death')
table(df$death2)
```

11. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)
```{r}
summary(df$Deaths)
```

12. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3
```{r}
df$death3 <- cut(df$Deaths, breaks=c(-Inf,358,7325,Inf),labels = c('low_death','mid_death','high_death'))
table(df$death3)
```

13. Find the average cases in Rhode Island in 2021
```{r}
df1 <- df[(df$State=='Rhode Island')&(df$Date>='2021-01-01'),]
mean(df1$Cases)
```

14. Find the median cases by weekdays in Rhode Island in 2021 
```{r}
df1 <- df[(df$State=='Rhode Island')&(df$Date>='2021-01-01'),]
by(df1$Cases, df1$Weekdays, median)
```

15. Compare the median cases in Rhode Island in June, July, August and September. 
```{r}
df$Month <- months(df$Date)
df2 <- df[(df$State=='Rhode Island')&(df$Date>='2021-06-01'),]
by(df2$Cases,df2$Month,median)
```

