
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 14: Twitters Mining with rtweet"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment14.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


[Sample Codes](rtweet2.html)

-------

1. Pick a keyword or hashtag. Download the data associated with the keyword/hashtag. Plot at least 10 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions. 
```{r}
library(rtweet)
library(tidytext)
library(ggpubr) 
library(tidyverse) 
library(knitr)
library(lubridate)

keyword_search = '#Patriots'

#df <- search_tweets(q = keyword_search, 
#n = 18000,
#                     include_rts = FALSE,
#                        `-filter` = "replies",
#                        lang = "en") %>% 
#  mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))

#write_csv(df, 'twitter_data_pats.csv')
df <- read_csv('twitter_data_pats.csv')
```

```{r}
df %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#Patriots",'#NewEngland','#patriots'), str_detect(hashtag, "^#")) %>%
  count(hashtag, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(hashtag, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
library(RColorBrewer)

pal <- brewer.pal(8,"Dark2")
library(wordcloud) 

df %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#Patriots",'#NewEngland','#patriots'), str_detect(hashtag, "^#")) %>%
  count(hashtag, sort = TRUE) %>%
  mutate(hashtag = str_remove(hashtag, '#')) %>% 
  with(wordcloud(hashtag, n, random.order = FALSE, max.words = 50, colors = pal))
```
```{r}
library(emo)
df %>%
  mutate(emoji = ji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(y=reorder(emoji,n), x=n)) +
  geom_col()+
  theme(axis.text.y = element_text(size = 40))+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  count(screen_name, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(screen_name, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(mentions, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  count(source, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(source, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  filter(!is.na(country)) %>% 
  count(country, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(country, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  filter(!is.na(location), !location=='') %>% 
  count(location, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(location, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  select(screen_name, favourites_count) %>% 
  filter(!is.na(favourites_count)) %>% 
  group_by(screen_name) %>% 
  summarise(average_fav = mean(favourites_count)) %>% 
  arrange(-average_fav) %>% 
  head(5) %>% 
  ggplot(aes(x=average_fav, y = reorder(screen_name, average_fav)))+
  geom_col()+
  labs(y='Account')
```
```{r}
ts_plot(df, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets",
       subtitle = paste0(format(min(df$created_at), "%d %B %Y"), " to ", format(max(df$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()
```

2. Choose a location then pick a trending keyword/hashtag in the location. Download the data associated with the keyword/hashtag. Plot at least 10 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions. 
```{r}
keyword_search = '#Celtics'

#df <- search_tweets(q = keyword_search, 
#                        n = 18000,
#                        include_rts = FALSE,
#                      `-filter` = "replies",
 #                       lang = "en",location='Boston') %>% #
 # mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))

#write_csv(df, 'twitter_data_celtics.csv')
df <- read_csv('twitter_data_celtics.csv')
```
```{r}
df %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#Celtics",'#Boston','#celtics'), str_detect(hashtag, "^#")) %>%
  count(hashtag, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(hashtag, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```

```{r}
library(RColorBrewer)

pal <- brewer.pal(8,"Dark2")
library(wordcloud) 

df %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#Celtics",'#Boston','#celtics'), str_detect(hashtag, "^#")) %>%
  count(hashtag, sort = TRUE) %>%
  mutate(hashtag = str_remove(hashtag, '#')) %>% 
  with(wordcloud(hashtag, n, random.order = FALSE, max.words = 50, colors = pal))
```
```{r}
df %>%
  mutate(emoji = ji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(y=reorder(emoji,n), x=n)) +
  geom_col()+
  theme(axis.text.y = element_text(size = 40))+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  count(screen_name, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(screen_name, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```

```{r}
df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(mentions, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```
```{r}
df %>% 
  count(source, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(source, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```

```{r}
df %>% 
  unnest_tokens(output = word, input = text, token = "words") %>%
  anti_join(get_stopwords()) %>% 
  count(word, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(word, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```

```{r}
ts_plot(df, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets",
       subtitle = paste0(format(min(df$created_at), "%d %B %Y"), " to ", format(max(df$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()
```
```{r}
df %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(y= reorder(sentiment, n), x = n))+geom_col()+
    labs(y='Relative Frequency', x ='')
```

```{r}
df %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("afinn")) %>%
    filter(!is.na(value)) %>%
    count(value, wt = n, sort = TRUE) %>% 
    ggplot(aes(x= value, y = n))+geom_col()+
    labs(y='Frequency', x ='')
```

